---
title: "Swirl Guidelines"
editor: visual
author: "rebdau"
editor: visual
---

## 1. Start swirl

Load the swirl package into your current R session. You will need to do this **every time** you start R or want to continue an old lesson or start a new lesson.

**Code you type in R:**

```{r, eval=FALSE}
library(swirl)
```

**Output you will see in the console:**

``` text
Hi! Type swirl() when you are ready to begin.
```

**Code you type in R:**

```{r, eval=FALSE}
swirl()
```

**Output you will see in the console:**

``` text
Welcome to swirl! Please sign in.
If you've been here before, use the same name as you did then.
If you are new, call yourself something unique.
What shall I call you? 
```

## 2. Enter your name

This name will allow the instructor to **identify you** when you have completed the lesson.

## 3. Choose a course

``` text
What shall I call you? manfroid.gerard 
| Please choose a course, or type 0 to exit swirl. 
1: STS ST07 swirl 
2: Take me to the swirl course repository!
Selection: 1 
```

We will be working through the lessons in the **‘STS_ST07’** course.\
Type `1` to select this course.

## 4. Choose a lesson

| Please choose a lesson, or type 0 to return to course menu.

``` text
Please choose a lesson, or type 0 to return to course menu.
1: Basic Building Blocks
2: Workspace Directories and Files
3: Data classes
4: Logic
5: Sequences of Numbers
6: Subsetting Vectors
7: Matrices and Data Frames
8: Lists
9: Lists example
10: lapply and sapply
11: vapply and tapply
12: Functions
13: Simulation
```

Choose the first lesson: **Basic Building Blocks**\
Type `1` to select this lesson.

## 5. Do the lesson

``` text
Attempting to load lesson dependencies...
Package ‘base64enc’ loaded correctly!
0%
In this lesson, we will explore some basic building blocks of the R programming language...
```

The screen also shows you your progress through the lesson (0%).

## 6. Submitting your lesson

You will need to be **connected to the internet** to submit your lesson.

When you are done, the last question will ask if you want to **submit your answers** to me to verify that you completed the lesson.

-   Enter the number of your response (usually `1`).\
-   This will open a **new web page**, a Google form.\
-   Scroll down and click **Submit**.

This will send an **encrypted response** to the Google form so that I can verify you completed the lesson.

Hit **Enter** to advance when presented with `…`.\

## Some useful commands for swirl

| Command  | Description                                                  |
|----------|--------------------------------------------------------------|
| `bye()`  | Exit swirl                                                   |
| `play()` | Leave swirl temporarily and gain access to the console again |
| `nxt()`  | Return to swirl after playing                                |
| `main()` | Return to the main menu                                      |
| `info()` | Display a list of these special commands                     |
